Efficient GPU implementation of multicomponent and multiphase Lattice Boltzmann models.

### 2010-04-05 paper.tex
Break lines in the remainder of the text.

\section{LBM}
\label{sec:lbm:binary:liquids}
This works concentrates on two popular LBM multiphase models. Originally introduced in 1993 \cite{Shan-chen:extended} the model attracted a multitude of researchers by its simplicity.  The free-energy model \cite{swift} is based on the free-energy phase transition \cite{landau}. Both models werre successfully applied in simulation of two-phase blood flow \cite{halliday-multicomponent}, flow in microchannels \cite{pooley-contact}, thermal flow \cite{zhang-thermal}, and studies of break-up of the liquid droplet \cite{nourgaliev-breakup}. The section describes the two-dimensional implementation of the Shan-Chen and free-energy models with the D2Q9 model.

@@

\subsection{Binary liquid multiphase model}
In this section we'd like to describe binary liquid model. Binary model is based on the free energy model \cite{swift,landau}:
\begin{equation}
\mathfrak{F}=\int{J \mathrm{d}V}=\int{\left(c_s^2\rho\ln\rho+\frac{A}{2}\phi^2+\frac{B}{4}\phi^4 + \frac{k}{2}(\nabla \phi)^2 \right)\mathrm{d}V},
\end{equation}
where coefficients $A$ and $B$ are responsible for the phase separation, coefficient $k$ is responsible for the surface tension between phases and $\phi$ is the order parameter. Different phases are corresponding to extreme values of $\phi$ as $-1$ and $1$.
The lattice Boltzmann model for the binary free-energy model is defined through two distribution sets:
\begin{equation}
\begin{aligned}
&f_i^{eq}=w_i \rho \biggl(1+\frac{u_{\alpha}c_{i\alpha}}{c_s^2}+\frac{Q_{i\alpha\beta}u_{\alpha}u_{\beta}}{2 c_s^4}\biggr), i=0\div8\\
&g_i^{eq}=w_i(\Gamma \mu + \frac{\phi c_{i\alpha} u_{i\alpha}}{c_s^2}+\phi^m \frac{Q_{i\alpha\beta}u_{\alpha}u_{\beta}}{2 c_s^4}), i\neq0 \\
&g_0^{eq}=\phi-\sum_{i\neq0}{g_i^{eq}}\quad,
\end{aligned}
\end{equation}
where $\Gamma$ is the mobility parameter, chemical potential $\mu=-A\phi+A\phi^3-k\Delta\phi$, $k$ is related to the surface tension. The macroscopic parameters are calculated as:
\begin{equation}
\begin{aligned}
\rho=\sum_i{f_i}\\
\rho u_{\alpha}=\sum_i{f_i c_{i\alpha}}\\
\phi=\sum_i{g_i}
\end{aligned}
\end{equation}
The equilibrium distribution functions lead to the macroscopic equations {\color{red} Give citation here}:
\begin{equation}
\begin{aligned}
&\partial_t \rho+ \partial_{\alpha} \rho u_{\alpha}=0\\
&\rho\left(\partial_t+u_{\beta}\partial_{\beta}\right) u_{\alpha}=\\
&-\partial_{\alpha}P_{\alpha \beta} + \nu\partial_{\beta}\left(\partial_{\alpha}u_{\beta}+\partial_{\beta} u_{\alpha} + \frac{1}{3}\partial_{\gamma} u_{\gamma} \delta_{\alpha\beta}\right)\\
&\partial_t \phi + \partial_{\alpha} \phi u_{\alpha}=D\Delta \mu,
\end{aligned}
\label{binary:fluid:system}
\end{equation}
with the bulk pressure $p_0=\rho c_s^2-\frac{B}{2}\phi^2+\frac{3}{4}B \phi^2$.

{\color{red} Michal, need your help here. Which parameters have you used for simulation. Please check above.}
We take equilibrium distribution function for the binary-liquid gas model. In general, it can be presented in the following form:
\subsection{Lattice Boltzmann implementation}
For all distribution functions the collision and streaming step are performed:
\begin{equation*}
\begin{aligned}
f_i^{\star}=(1-\omega)f_i+f_i^{eq}\\
f_i(\bm{x}+\bm{c_i})=f_i^{\star}. 
\end{aligned}
\end{equation*}

>>>>

\section{The Lattice-Boltzmann method}
\label{sec:lbm:binary:liquids}
This works concentrates on two popular LBM multiphase models. Originally introduced
in 1993 \cite{Shan-chen:extended} the model attracted a multitude of researchers
by its simplicity.  The free-energy model \cite{swift} is based on the free-energy
phase transition \cite{landau}. Both models werre successfully applied in simulation
of two-phase blood flow \cite{halliday-multicomponent}, flow in microchannels
\cite{pooley-contact}, thermal flow \cite{zhang-thermal}, and studies of break-up
of the liquid droplet \cite{nourgaliev-breakup}. The section describes the
two-dimensional implementation of the Shan-Chen and free-energy models with
the D2Q9 model.

@@

\subsection{Binary liquid multiphase model}
In this section we describe the binary liquid model. Binary model is based on
the free energy model \cite{swift,landau}:
\begin{equation}
\mathfrak{F}=\int{J \mathrm{d}V}=\int{\left(c_s^2\rho\ln\rho+\frac{A}{2}\phi^2+\frac{B}{4}\phi^4 + \frac{k}{2}(\nabla \phi)^2 \right)\mathrm{d}V},
\end{equation}
where coefficients $A$ and $B$ are responsible for the phase separation,
coefficient $k$ is responsible for the surface tension between phases and
$\phi$ is the order parameter. Different phases are corresponding to
extreme values of $\phi$ as $-1$ and $1$.
The lattice Boltzmann model for the binary free-energy model is defined
through two distribution sets:
\begin{equation}
\begin{aligned}
&f_i^{eq}=w_i \rho \biggl(1+\frac{u_{\alpha}c_{i\alpha}}{c_s^2}+\frac{Q_{i\alpha\beta}u_{\alpha}u_{\beta}}{2 c_s^4}\biggr), i=0\div8\\
&g_i^{eq}=w_i(\Gamma \mu + \frac{\phi c_{i\alpha} u_{i\alpha}}{c_s^2}+\phi^m \frac{Q_{i\alpha\beta}u_{\alpha}u_{\beta}}{2 c_s^4}), i\neq0 \\
&g_0^{eq}=\phi-\sum_{i\neq0}{g_i^{eq}}\quad,
\end{aligned}
\end{equation}
where $\Gamma$ is the mobility parameter, chemical potential
$\mu=-A\phi+A\phi^3-k\Delta\phi$, $k$ is related to the surface
tension. The macroscopic parameters are calculated as:
\begin{equation}
\begin{aligned}
\rho=\sum_i{f_i}\\
\rho u_{\alpha}=\sum_i{f_i c_{i\alpha}}\\
\phi=\sum_i{g_i}
\end{aligned}
\end{equation}
The equilibrium distribution functions lead to the macroscopic equations
{\color{red} Give citation here}:
\begin{equation}
\begin{aligned}
&\partial_t \rho+ \partial_{\alpha} \rho u_{\alpha}=0\\
&\rho\left(\partial_t+u_{\beta}\partial_{\beta}\right) u_{\alpha}=\\
&-\partial_{\alpha}P_{\alpha \beta} + \nu\partial_{\beta}\left(\partial_{\alpha}u_{\beta}+\partial_{\beta} u_{\alpha} + \frac{1}{3}\partial_{\gamma} u_{\gamma} \delta_{\alpha\beta}\right)\\
&\partial_t \phi + \partial_{\alpha} \phi u_{\alpha}=D\Delta \mu,
\end{aligned}
\label{binary:fluid:system}
\end{equation}
with the bulk pressure $p_0=\rho c_s^2-\frac{B}{2}\phi^2+\frac{3}{4}B \phi^2$.

{\color{red} Michal, need your help here. Which parameters have you used for simulation. Please check above.}
We take equilibrium distribution function for the binary-liquid gas model. In general, it can be presented in the following form:

\subsection{Lattice Boltzmann implementation}
For all distribution functions the collision and streaming step are performed:
\begin{equation*}
\begin{aligned}
f_i^{\star}=(1-\omega)f_i+f_i^{eq}\\
f_i(\bm{x}+\bm{c_i})=f_i^{\star}. 
\end{aligned}
\end{equation*}
